Bandit Multiclass Classification

### 2018-10-16 ptf_margin.tex
a pass over ptf_margin

\section{Construction of polynomials}
Our $\phi$'s in considerations are as follows:
\begin{enumerate}
%\sqrt{\frac{1}{\deg+1}}
\item $\phi_{s}(x) = ( x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq s, i_1, \ldots, i_d \geq 0} = (x_S)_{S \in N^d, \|S\|_1 \leq s}$. This corresponds to the complete symmetric kernel $K_s$. Note that for all $x$ such that $\| x \|_2 \leq 1$,
$\inner{\phi_{s}(x), \phi_{s}(x)} \leq \sum_{i=0}^s \|x\|^{2i} \leq 1 + s$.

@@

For a polynomial $p = \sum_{S \in \fN^d} c_S x_S$, define $\|p\|$, the norm of $p$, as the $\ell_2$ norm of the vector that contains its coefficients on every monomial, that is $\|p\| = \| (c_S)_{S \in \fN^d} \| = \sqrt{\sum_{S \in \fN^d} c_S^2}$. We have the following simple result.
\begin{lemma}
Suppose polynomial $p$ has degree $\deg$, and has norm $\|p\|$. Then
\begin{enumerate}
\item For any degree $s \geq \deg$, $p$ can be written as $\inner{c, \phi_s(x)}$, where $\|c\| = \|p\|$.
\item For any degree $s \geq \deg$, $p$ can be written as $\inner{c', \phi_s'(x)}$, where $\|c_0\| \leq \|p\|$.
\item $p$ can be written as $\inner{c_0, \phi_0(x)}$, where $\|c_0\| \leq 2^{\frac{\deg}{2}} \|p\|$.
\end{enumerate}
\end{lemma}
\begin{proof}
Note that $p(x)$ can be written as $\sum_{i_1,\ldots,i_d \in \fN} c_{i_1,\ldots,i_d} x_1^{i_1} \ldots x_d^{i_d}$. As $p$ has degree $\deg$, $c_{i_1,\ldots,i_d} = 0$ for $i_1 + \ldots + i_d > \deg$.

The first item follows as $\phi_s(x)$ contains all monomials in $p$.

For the second item, we define $(c')_{i_1,\ldots,i_d} = \frac{c_{i_1,\ldots,i_d}}{\sqrt{ {s \choose i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}}$ for all $(i_1,\ldots,i_d) \in \fN, i_1+\ldots+i_d \leq s$. It can be seen that $\inner{c', \phi_s'(x)} = \inner{c, \phi_s(x)}$, and
$\| c' \| \leq \| c \| = \| p \|$.

@@

\subsection{Construction using rational functions}
\paragraph{The construction.} Define rational function
\[
  Q(x) = \sum_{i=1}^t S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) - (t - \frac 1 2).
\]
where function
\[
S_n^k(x) = \frac{P_n(-x)^{h(k)} - P_n(x)^{h(k)}}{P_n(-x)^{h(k)} + P_n(x)^{h(k)}},
\]
$h(k)$ is the smallest odd integer greater than $\log(2k+1)$, and $P_n(x) = (x - 1) \cdot \prod_{i=1}^n (x - 2^i)^2$.

Now denote by $A_n^k(x) = P_n(x)^{h(k)} - P_n(-x)^{h(k)}$, $B_n^k(x) = -P_n(-x)^{h(k)} - P_n(x)^{h(k)}$.
\cz{Note the difference between this line and KS04 - we multiply by $B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}\gamma)$ as opposed to its square. The latter would also work, but it will make the equations more cumbersome.}
Define polynomial $p$ as
\begin{eqnarray*}
  p(x) &:=& \sum_{i=1}^t A_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) \cdot \prod_{j \neq i} B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) - (t-\frac12) \prod_{j=1}^t B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma})
\end{eqnarray*}

@@

\begin{lemma}[~\cite{klivans2004learning}]
For all $(x,y)$ in $S$ satisfying Definition~\ref{def:int-margin}, we have that $y Q(x) \geq \frac 1 2$.
As a consequence, $y p(x) \geq 2^{n(n-1)h(2t)t - 2}$.
\end{lemma}
\begin{proof}
We consider two cases regarding the label of the example.
\begin{enumerate}
\item Suppose $y = 1$, then for all $i$ in $[t]$, $v_i \cdot x \in [\gamma, 1]$. This implies that $\frac{v_i \cdot x}{\gamma} \in [1, \frac 1 \gamma]$.
By item~\ref{item:sign-rt} of Fact~\ref{fact:newman}, we have that $D_i(x) \in [1, 1+ \frac 1 {2t}]$.
Hence, $Q(x) \geq t - (t - \frac 1 2) \geq \frac 1 2$.

\item Suppose $y = -1$. First observe that for all $i$ in $[t]$, $\frac{v_i \cdot x}{\gamma} \in [-\frac 1\gamma, \frac 1 \gamma]$. By items~\ref{item:sign-rt},
~\ref{item:sign-lt} and~\ref{item:sign-mid} of Fact~\ref{fact:newman}, we have that $S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) \leq 1+ \frac 1 {2t}$.
In addition, by Definition~\ref{def:int-margin}, there exists an $i_0$ in $[t]$, such that $v_{i_0} \cdot x \leq -\gamma$.
By item~\ref{item:bound-out} of Fact~\ref{fact:cheb}, we have that
$D_{i_0}(x) \in [-1 - \frac 1 {2t}, -1]$.
Hence,
\[ Q(x) = D_{i_0}(x) + \sum_{i \neq i_0} D_i(x) - (t - \frac 1 2)
\leq -1 + (t-1)(1 + \frac 1 {2t}) - (t - \frac 1 2) \leq - \frac 1 2. \]
%\leq -1 + t-1 + \frac{t-1}{2t} - (t - \frac 1 2)
\end{enumerate}
To summarize, we have shown that for all $(x,y)$ in $S$, $y Q(x) \geq \frac 1 2$.
Therefore,
\[ y p(x) = y Q(x) \cdot \prod_{i=1}^t B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}\gamma) \geq \frac 1 2 ((1-\frac{1}{4t+1}) \cdot 2^{n(n-1)h(2t)})^t \geq 2^{n(n-1)h(2t)t - 2}. \]
\end{proof}

\begin{fact}
$S_n^k(\cdot)$ has the following properties:
\begin{enumerate}
\item If $x$ is in $[1, 2^n]$, then $S_n^k(x)$ is in $[1, 1 + \frac 1 k]$. \label{item:sign-rt}
\item If $x$ is in $[-2^{-n}, -1]$, then $S_n^k(x)$ is in $[-1 - \frac 1 k, -1]$. \label{item:sign-lt}
\item If $x$ is in $[-1, 1]$, then $|S_n^k(x)|$ is in $[-1, 1]$. \label{item:sign-mid}
\cz{This fact is based on discussions with Chen-Yu, which we found important but was omitted by~\cite{klivans2004learning}.}
\item For all $x$ in $[-2^{-n}, 2^{-n}]$, $B_n^k(x) \geq (1-\frac{1}{2k+1}) \cdot 2^{n(n-1)h(k)}$.
\cz{This is a refined lower bound of Lemma 6 of~\cite{klivans2004learning}; we got rid of the weird
requirement that ``the fractional part of $x$ is at least $2^{-n}$''.}
\label{item:sign-denom}
\end{enumerate}
\label{fact:newman}
\end{fact}
\begin{proof}
We prove all the items accordingly.
\begin{enumerate}
\item Observe that $S_n^k(x)$ can be written as:
\[ S_n^k(x) = \frac{1 + (-\frac{P_n(x)}{P_n(-x)})^{h(k)}}{ 1 - (-\frac{P_n(x)}{P_n(-x)})^{h(k)} }.  \]
Denote by $r = (-\frac{P_n(x)}{P_n(-x)})^{h(k)}$. By item~\ref{item:x-large} of Fact~\ref{fact:pn}, $r \in [0, \frac{1}{2k+1}]$. This implies that
$S_n^k(x) = \frac{1+r}{1-r} \in [1, 1 + \frac 1 k]$.

@@

\item Noticing that $B_n^k(x)$ is an even function, without loss of generality, suppose $x \geq 0$.
First, note that if $x \geq 0$, then $\abs{P_n(-x)} \geq \prod_{i=1}^n 2^{2i} = 2^{n(n-1)}$.
If $x$ is in $[1,2^n]$, then $B_n^k(x) = \abs{P_n(-x)^{h(k)}} (1 - r) \geq \abs{P_n(-x)^{h(k)}} \cdot \frac{2k}{2k+1} \geq 2^{n(n-1)h(k)} \cdot \frac{2k}{2k+1}$.
If $x$ is in $[0,1]$, as both $P_n(-x)$ and $-P_n(x)$ are $\leq 0$, we have $B_n^k(x) \geq \abs{P_n(-x)^{h(k)}} \geq 2^{n(n-1)h(k)}$. Therefore, for all $x \in [0,2^n]$,
$\abs{B_n^k(x)} \geq (1-\frac{1}{2k+1}) 2^{n(n-1)h(k)}$.
\end{enumerate}
\end{proof}

\paragraph{Norm bound.} We bound the norm of $p$ in the theorem below.
\begin{theorem}
$p(x)$ has degree $\deg = (2\ceil{\log \frac 1 \gamma}+1)h(2t)t$, and has norm $\|p\| \leq ((16\ceil{\log \frac 1 \gamma}+8) h(2t) t \cdot \frac 1 \gamma)^{(2\ceil{\log \frac 1 \gamma}+1)h(2t)t}$.
\end{theorem}
\begin{proof}
The degree of $p$ follows from the
Let $n = \ceil{\log \frac 1 \gamma}$.

@@

\begin{fact}
The following is true:
\begin{enumerate}
\item If $x \in [0,1]$, then $0 \leq -P_n(x) \leq -P_n(-x)$. \label{item:x-small}
\item If $x \in [1, 2^n]$, then $0 \leq 4P_n(x) \leq -P_n(-x)$. \label{item:x-large}
\end{enumerate}
\label{fact:pn}
\end{fact}
\begin{proof}
First, observe that for any $x \geq 0$, for all $i$, $(x+2^i)^2 \geq (x - 2^i)^2$ holds.

For the first item, given that $x \in [0,1]$, $1+x \geq 1-x \geq 0$. Therefore,
\[ \frac{-P_n(-x)}{-P_n(x)} = \frac{1+x}{1-x} \prod_{i =1}^n \frac{(x+2^i)^2}{(x - 2^i)^2}  \geq 1. \]

For the second item, given that $x \geq 1$, $1+x \geq x-1 \geq 0$. In addition, as $x$ is in $[1,2^n]$, there exists an $i_0 \in [n]$ such that $2^{i_0-1} \leq x \leq 2^i_0$. Therefore,
$(x+2^i)^2 \geq 4(x - 2^i)^2$. Hence,
\[ \frac{-P_n(-x)}{P_n(x)} = \frac{1+x}{ x-1} \frac{(x+2^{i_0})^2}{(x - 2^{i_0})^2} \prod_{i \neq i_0} \frac{(x+2^i)^2}{(x - 2^i)^2} \geq 4. \]
\end{proof}

\subsection{Construction using Chebyshev polynomials}
\paragraph{The construction.} Define
\[ p(x) = t + \frac 1 2 - \sum_{i=1}^t (T_{\ceil{\sqrt{\frac 1 \gamma}}}(1 - v_i \cdot x))^{\ceil{\log 2t}}, \]
where
$T_r(\cdot)$ is the $r$-th order Chebyshev polynomial. Denote by $C_i(x) = (T_{\ceil{\sqrt{\frac 1 \gamma}}}(1 - v_i \cdot x))^{\ceil{\log 2t}}$. $p$ can therefore be simplified to
\[ p(x) = t + \frac 1 2 - \sum_{i=1}^t C_i(x). \]

\begin{lemma}[~\cite{klivans2004learning}]
For all $(x,y)$ in $S$ satisfying Definition~\ref{def:int-margin}, we have that $y p(x) \geq \frac 1 2$.
\end{lemma}
\begin{proof}
We consider the two cases regarding the label of the example.
\begin{enumerate}
\item Suppose $y = 1$, then for all $i$ in $[t]$, $v_i \cdot x \geq \gamma$. This implies that for all
$i$ in $[t]$, $1 - v_i \cdot x \in [0, 1-\gamma]$. By item~\ref{item:bound-in} of Fact~\ref{fact:cheb}, we have that for all $i$, $|C_i(x)| \leq 1$.
Therefore, $p(x) \geq t + \frac 1 2 - t \geq \frac 1 2$.

\item Suppose $y = -1$. First observe that for all $i$, $T_{\ceil{\sqrt{\frac 1 \gamma}}}(1 - v_i \cdot x)) \geq -1$. This is because of items~\ref{item:bound-in} and~\ref{item:bound-out} of Fact~\ref{fact:cheb}.
This implies that $C_i(x) \geq -1$.
On the other hand, by Definition~\ref{def:int-margin}, there exists an $i_0$ in $[t]$, such that $v_{i_0} \cdot x \leq -\gamma$. By item~\ref{item:bound-out} of Fact~\ref{fact:cheb}, we have that
$C_{i_0}(x) \geq (1 + \gamma \cdot \frac 1 \gamma)^{\ceil{\log 2t}} \geq 2t$. Therefore,
\[ p(x) = t + \frac 1 2 - C_{i_0}(x) - \sum_{i \neq i_0} C_i(x) \leq t + \frac 1 2 - 2t + (t-1) \leq -\frac 1 2. \]
\end{enumerate}
\end{proof}

@@

\paragraph{Norm bound.} We bound the norm of $p$ in the theorem below.
\begin{theorem}
$p(x)$ has degree $\deg = \ceil{\sqrt{\frac1\gamma}} \cdot \ceil{\log(2t)}$, and has norm $\|p\| \leq 2 \cdot (256 \ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t})^{\ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t}}$.
\end{theorem}
\begin{proof}
Denote by $r = \ceil{\sqrt{\frac1\gamma}}$.
First, for all $i$, as $v_i$ has norm at most 1,
\[ \| (1 - v_i \cdot x) \|^2 \leq 2. \]
Therefore, by Lemma~\ref{lem:norm-oper},
\[ \| c_l (1 - v_i \cdot x)^l \|^2 = c_l^2 \| (1 - v_i \cdot x)^l \|_2^2 \leq 2^{2r} l^l 2^l. \]
Hence,
\[ \| T_r(1 - v_i \cdot x) \|^2 = \| \sum_{l=0}^r c_l (1 - v_i \cdot x)^l \|^2 \leq (r+1) \cdot \sum_{l=0}^r 2^{2r} l^l 2^l \leq (r+1)^2 (8r)^r \leq (32r)^r. \]
where the last inequality uses the fact that $(r+1)^2 \leq 2^r$.
And by Lemma~\ref{lem:norm-oper},
\[ \| C_r(x) \|^2 \leq (\ceil{\log 2t})^{\ceil{\log 2t} r} \cdot ((32r)^r)^{\ceil{\log 2t}}. \]
Therefore,
\[ \| p(x) \|^2 \leq (t+1) \cdot ((t+\frac 1 2)^2 + t (32 r\ceil{\log 2t})^{\ceil{\log 2t} r}) \leq 2 \cdot (256 r \ceil{\log 2t})^{r \ceil{\log 2t}}  \]
where the last inequality uses the fact that $(t+1)((t+\frac12)^2+t) \leq 2 \cdot 8^{\ceil{\log 2t}}$ and algebra.
%$2^{2r \ceil{\log 2t}} \geq \max(2t^2, r^2)$.
\end{proof}

@@

@@

>>>>

\section{Construction of large margin feature mappings using polynomials}
Our $\phi$'s in considerations are as follows:
\begin{enumerate}
%\sqrt{\frac{1}{\deg+1}}
\item $\phi_{s}(x) = ( x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq s, i_1, \ldots, i_d \geq 0} = (x_S)_{S \in \fN^d, \|S\|_1 \leq s}$. This corresponds to the complete symmetric kernel $K_s$. Note that for all $x$ such that $\| x \|_2 \leq 1$,
$\inner{\phi_{s}(x), \phi_{s}(x)} \leq \sum_{i=0}^s \|x\|^{2i} \leq 1 + s$.

@@

For a polynomial $p = \sum_{S \in \fN^d} c_S x_S$, define $\|p\|$, the norm of $p$, as the $\ell_2$ norm of the vector that contains its coefficients on every monomial, that is $\|p\| = \| (c_S)_{S \in \fN^d} \| = \sqrt{\sum_{S \in \fN^d} c_S^2}$. We have the following simple result.
\begin{lemma}
Suppose polynomial $p$ has degree $\deg$, and has norm $\|p\|$. Then
\begin{enumerate}
\item For any degree $s \geq \deg$, $p$ can be written as $\inner{c, \phi_s(x)}$, where $\|c\| = \|p\|$.
\item For any degree $s \geq \deg$, $p$ can be written as $\inner{c', \phi_s'(x)}$, where $\|c'\| \leq \|p\|$.
\item $p$ can be written as $\inner{c_0, \phi_0(x)}$, where $\|c_0\| \leq 2^{\frac{\deg}{2}} \|p\|$.
\end{enumerate}
\end{lemma}
\label{lem:fm-convert}
\begin{proof}
Note that $p(x)$ can be written as $\sum_{i_1,\ldots,i_d \in \fN} c_{i_1,\ldots,i_d} x_1^{i_1} \ldots x_d^{i_d}$. As $p$ has degree $\deg$, $c_{i_1,\ldots,i_d} = 0$ for $i_1 + \ldots + i_d > \deg$.

The first item follows as $\phi_s(x)$ contains all monomials of degree at most $s$, which in turn contains all monomials in $p$.

For the second item, we define $(c')_{i_1,\ldots,i_d} = \frac{c_{i_1,\ldots,i_d}}{\sqrt{ {s \choose i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}}$ for all $(i_1,\ldots,i_d) \in \fN$. It can be seen that $\inner{c', \phi_s'(x)} = \inner{c, \phi_s(x)}$, and
$\| c' \| \leq \| c \| = \| p \|$.

@@

\subsection{Large margin polynomial via rational functions}
\paragraph{The construction.} Define rational function
\[
  Q(x) = \sum_{i=1}^t S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) - (t - \frac 1 2).
\]
where for $k,n$ in $\fN$, function
\[
S_n^k(x) = \frac{P_n(-x)^{h(k)} - P_n(x)^{h(k)}}{P_n(-x)^{h(k)} + P_n(x)^{h(k)}},
\]
$h(k)$ is the smallest odd integer greater than $\log(2k+1)$, and $P_n(x) = (x - 1) \cdot \prod_{i=1}^n (x - 2^i)^2$.

Now denote by $A_n^k(x) = P_n(x)^{h(k)} - P_n(-x)^{h(k)}$, $B_n^k(x) = -P_n(-x)^{h(k)} - P_n(x)^{h(k)}$.
Also, define $D_i(x) = S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma})$.

\cz{Note the difference between this line and KS04 - we multiply by $B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}\gamma)$ as opposed to its square. The latter would also work, but it will make the equations more cumbersome.}
Define polynomial $p$ as
\begin{eqnarray*}
  p(x) &:=& \sum_{i=1}^t A_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) \cdot \prod_{j \neq i} B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) - (t-\frac12) \prod_{j=1}^t B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma})
\end{eqnarray*}

@@

\begin{lemma}[\cite{klivans2004learning}]
For all $(x,y)$ in $S$ satisfying Definition~\ref{def:int-margin}, we have that $y Q(x) \geq \frac 1 2$.
As a consequence, $y p(x) \geq 2^{\ceil{\log \frac 1 \gamma}(\ceil{\log \frac 1 \gamma}-1)h(2t)t - 2}$.
\label{lem:rational-margin}
\end{lemma}
\begin{proof}
We consider two cases regarding the label of the example.
\begin{enumerate}
\item Suppose $y = 1$, then for all $i$ in $[t]$, $v_i \cdot x \in [\gamma, 1]$. This implies that $\frac{v_i \cdot x}{\gamma} \in [1, \frac 1 \gamma]$.
By item~\ref{item:sign-rt} of Fact~\ref{fact:newman}, we have that $D_i(x) \in [1, 1+ \frac 1 {2t}]$.
Hence, $Q(x) \geq t - (t - \frac 1 2) \geq \frac 1 2$.

\item Suppose $y = -1$. First observe that for all $i$ in $[t]$, $\frac{v_i \cdot x}{\gamma} \in [-\frac 1\gamma, \frac 1 \gamma]$. By items~\ref{item:sign-rt},
~\ref{item:sign-lt} and~\ref{item:sign-mid} of Fact~\ref{fact:newman}, we have that $S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) \leq 1+ \frac 1 {2t}$.
In addition, by Definition~\ref{def:int-margin}, there exists an $i_0$ in $[t]$, such that $v_{i_0} \cdot x \leq -\gamma$.
By item~\ref{item:sign-lt} of Fact~\ref{fact:newman}, we have that
$D_{i_0}(x) \in [-1 - \frac 1 {2t}, -1]$.
Hence,
\[ Q(x) = D_{i_0}(x) + \sum_{i \neq i_0} D_i(x) - (t - \frac 1 2)
\leq -1 + (t-1)(1 + \frac 1 {2t}) - (t - \frac 1 2) \leq - \frac 1 2. \]
%\leq -1 + t-1 + \frac{t-1}{2t} - (t - \frac 1 2)
\end{enumerate}
To summarize, we have shown that for all $(x,y)$ in $S$, $y Q(x) \geq \frac 1 2$.
Therefore, by item~\ref{item:sign-denom} of Fact~\ref{fact:newman}, 
\[ y p(x) = y Q(x) \cdot \prod_{i=1}^t B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}\gamma) \geq \frac 1 2 ((1-\frac{1}{4t+1}) \cdot 2^{n(n-1)h(2t)})^t \geq 2^{n(n-1)h(2t)t - 2}. \]
\end{proof}

\begin{fact}
For $k, n$ in $\fN$, $S_n^k(\cdot)$ has the following properties:
\begin{enumerate}
\item If $x$ is in $[1, 2^n]$, then $S_n^k(x)$ is in $[1, 1 + \frac 1 k]$. \label{item:sign-rt}
\item If $x$ is in $[-2^{-n}, -1]$, then $S_n^k(x)$ is in $[-1 - \frac 1 k, -1]$. \label{item:sign-lt}
\item If $x$ is in $[-1, 1]$, then $|S_n^k(x)|$ is in $[-1, 1]$. \label{item:sign-mid}
\cz{This fact is based on discussions with Chen-Yu, which we found important but was omitted by~\cite{klivans2004learning}.}
\item For all $x$ in $[-2^{n}, 2^{n}]$, $B_n^k(x) \geq (1-\frac{1}{2k+1}) \cdot 2^{n(n-1)h(k)}$.
\cz{This is a refined lower bound of Lemma 6 of~\cite{klivans2004learning}; we got rid of the weird
requirement that ``the fractional part of $x$ is at least $2^{-n}$''.}
\label{item:sign-denom}
\end{enumerate}
\label{fact:newman}
\end{fact}
\begin{proof}
We prove all the items accordingly.
\begin{enumerate}
\item Observe that $S_n^k(x)$ can be written as:
\[ S_n^k(x) = \frac{1 + (-\frac{P_n(x)}{P_n(-x)})^{h(k)}}{ 1 - (-\frac{P_n(x)}{P_n(-x)})^{h(k)} }.  \]
Denote by $r = (-\frac{P_n(x)}{P_n(-x)})^{h(k)}$. By item~\ref{item:x-large} of Fact~\ref{fact:pn}, $r \in [0, \frac{1}{2k+1}]$. This implies that
$S_n^k(x) = \frac{1+r}{1-r} \in [1, 1 + \frac 1 k]$.

@@

\item Noticing that $B_n^k(x)$ is an even function, without loss of generality, suppose $x \geq 0$.
First, note that if $x \geq 0$, then $\abs{P_n(-x)} \geq \prod_{i=1}^n 2^{2i} = 2^{n(n-1)}$.
If $x$ is in $[1,2^n]$, then $B_n^k(x) = (-P_n(-x))^{h(k)} (1 - r) \geq (-P_n(-x))^{h(k)} \cdot \frac{2k}{2k+1} \geq 2^{n(n-1)h(k)} \cdot \frac{2k}{2k+1}$.
If $x$ is in $[0,1]$, as both $P_n(-x)$ and $-P_n(x)$ are $\leq 0$, we have $B_n^k(x) \geq (-P_n(-x))^{h(k)} \geq 2^{n(n-1)h(k)}$. Therefore, for all $x \in [0,2^n]$,
$B_n^k(x) \geq (1-\frac{1}{2k+1}) 2^{n(n-1)h(k)}$.
\end{enumerate}
\end{proof}

\begin{fact}
The following are true:
\begin{enumerate}
\item If $x \in [0,1]$, then $0 \leq -P_n(x) \leq -P_n(-x)$. \label{item:x-small}
\item If $x \in [1, 2^n]$, then $0 \leq 4P_n(x) \leq -P_n(-x)$. \label{item:x-large}
\end{enumerate}
\label{fact:pn}
\end{fact}
\begin{proof}
First, observe that for any $x \geq 0$, for all $i$, $(x+2^i)^2 \geq (x - 2^i)^2$ holds.

For the first item, given that $x \in [0,1]$, $1+x \geq 1-x \geq 0$. Therefore,
\[ \frac{-P_n(-x)}{-P_n(x)} = \frac{1+x}{1-x} \cdot \prod_{i =1}^n \frac{(x+2^i)^2}{(x - 2^i)^2}  \geq 1. \]

For the second item, given that $x \geq 1$, $1+x \geq x-1 \geq 0$. In addition, as $x$ is in $[1,2^n]$, there exists an $i_0 \in [n]$ such that $2^{i_0-1} \leq x \leq 2^i_0$. Therefore,
$(x+2^i)^2 \geq 4(x - 2^i)^2$. Hence,
\[ \frac{-P_n(-x)}{P_n(x)} = \frac{1+x}{ x-1} \cdot \frac{(x+2^{i_0})^2}{(x - 2^{i_0})^2} \cdot \prod_{i \neq i_0} \frac{(x+2^i)^2}{(x - 2^i)^2} \geq 4. \]
\end{proof}

\paragraph{Norm bound.} We bound the norm of $p$ in the theorem below.
\begin{theorem}
$p(x)$ has degree $\deg = (2\ceil{\log \frac 1 \gamma}+1)h(2t)t$, and has norm $\|p\| \leq ((16\ceil{\log \frac 1 \gamma}+8) h(2t) t \cdot \frac 1 \gamma)^{(2\ceil{\log \frac 1 \gamma}+1)h(2t)t}$.
\label{thm:rational-norm}
\end{theorem}
\begin{proof}
The degree of $p$ follows from the
Let $n = \ceil{\log \frac 1 \gamma}$.

@@

\subsection{Large margin polynomials via Chebyshev polynomials}
\paragraph{The construction.} Define
\[ p(x) = t + \frac 1 2 - \sum_{i=1}^t (T_{\ceil{\sqrt{\frac 1 \gamma}}}(1 - v_i \cdot x))^{\ceil{\log 2t}}, \]
where
$T_r(\cdot)$ is the $r$-th order Chebyshev polynomial. Denote by $C_i(x) = (T_{\ceil{\sqrt{\frac 1 \gamma}}}(1 - v_i \cdot x))^{\ceil{\log 2t}}$. $p$ can therefore be simplified to
\[ p(x) = t + \frac 1 2 - \sum_{i=1}^t C_i(x). \]

\begin{lemma}[\cite{klivans2004learning}]
For all $(x,y)$ in $S$ satisfying Definition~\ref{def:int-margin}, we have that $y p(x) \geq \frac 1 2$.
\label{lem:cheb-margin}
\end{lemma}
\begin{proof}
We consider the two cases regarding the label of the example.
\begin{enumerate}
\item Suppose $y = 1$, then for all $i$ in $[t]$, $v_i \cdot x \geq \gamma$. This implies that for all
$i$ in $[t]$, $1 - v_i \cdot x \in [0, 1-\gamma]$. By item~\ref{item:bound-in} of Fact~\ref{fact:cheb}, we have that for all $i$, $|C_i(x)| \leq 1$.
Therefore, $p(x) \geq t + \frac 1 2 - t \geq \frac 1 2$.

\item Suppose $y = -1$. First observe that for all $i$, $T_{\ceil{\sqrt{\frac 1 \gamma}}}(1 - v_i \cdot x) \geq -1$. This is because of items~\ref{item:bound-in} and~\ref{item:bound-out} of Fact~\ref{fact:cheb}, and that $1 - v_i \cdot x \geq 0$.
This implies that $C_i(x) \geq -1$.
On the other hand, by Definition~\ref{def:int-margin}, there exists an $i_0$ in $[t]$, such that $v_{i_0} \cdot x \leq -\gamma$. By item~\ref{item:bound-out} of Fact~\ref{fact:cheb}, we have that
$C_{i_0}(x) \geq (1 + \gamma \cdot \frac 1 \gamma)^{\ceil{\log 2t}} \geq 2t$. Therefore,
\[ p(x) = t + \frac 1 2 - C_{i_0}(x) - \sum_{i \neq i_0} C_i(x) \leq t + \frac 1 2 - 2t + (t-1) \leq -\frac 1 2. \]
\end{enumerate}
\end{proof}

@@

\paragraph{Norm bound.} We bound the norm of $p$ in the theorem below.
\begin{theorem}
$p(x)$ has degree $\deg = \ceil{\sqrt{\frac1\gamma}} \cdot \ceil{\log(2t)}$, and has norm $\|p\| \leq 2 \cdot (256 \ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t})^{\ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t}}$.
\label{thm:cheb-norm}
\end{theorem}
\begin{proof}
Denote by $r = \ceil{\sqrt{\frac1\gamma}}$.
First, for all $i$, as $v_i$ has norm at most 1,
\[ \| (1 - v_i \cdot x) \|^2 \leq 2. \]
Therefore, by Lemma~\ref{lem:norm-oper},
\[ \| c_l (1 - v_i \cdot x)^l \|^2 = c_l^2 \| (1 - v_i \cdot x)^l \|^2 \leq 2^{2r} l^l 2^l. \]
Hence,
\[ \| T_r(1 - v_i \cdot x) \|^2 = \| \sum_{l=0}^r c_l (1 - v_i \cdot x)^l \|^2 \leq (r+1) \cdot \sum_{l=0}^r 2^{2r} l^l 2^l \leq (r+1)^2 (8r)^r \leq (32r)^r. \]
where the last inequality uses the fact that $(r+1)^2 \leq 2^r$.
And by Lemma~\ref{lem:norm-oper},
\[ \| C_r(x) \|^2 \leq (\ceil{\log 2t})^{\ceil{\log 2t} r} \cdot ((32r)^r)^{\ceil{\log 2t}}. \]
Therefore,
\[ \| p(x) \|^2 \leq (t+1) \cdot ((t+\frac 1 2)^2 + t (32 r\ceil{\log 2t})^{\ceil{\log 2t} r}) \leq 2 \cdot (256 r \ceil{\log 2t})^{r \ceil{\log 2t}}  \]
where the last inequality uses the fact that $(t+1)((t+\frac12)^2+t) \leq 2 \cdot 8^{\ceil{\log 2t}}$ and algebra.
%$2^{2r \ceil{\log 2t}} \geq \max(2t^2, r^2)$.
\end{proof}

@@

\begin{proof}
\begin{enumerate}
\item From Lemma~\ref{lem:rational-margin} and Theorem~\ref{thm:rational-norm}, 
along with the fact that $s \geq (2\ceil{\log \frac 1 \gamma}+1) h(2t) t$,
we know that there exists some polynomial $p = \inner{c, \phi_s(x)}$, such that
$y \inner{c, \phi_s(x)} \geq  2^{\ceil{\log \frac 1 \gamma}(\ceil{\log \frac 1 \gamma}-1)h(2t)t - 2}$ and 
$\|c\| \leq ((16\ceil{\log \frac 1 \gamma}+8) h(2t) t \cdot \frac 1 \gamma)^{(2\ceil{\log \frac 1 \gamma}+1)h(2t)t}$. This implies that $S'$ is separable by a halfspace with the desired margin.

\item From Lemma~\ref{lem:cheb-margin} and Theorem~\ref{thm:cheb-norm},
along with the fact that $s \geq \ceil{\sqrt{\frac1\gamma}} \cdot \ceil{\log(2t)}$, we know that there exists some polynomial $p = \inner{c, \phi_s(x)}$, such that
$y \inner{c, \phi_s(x)} \geq \frac 1 2$ and
$\| c \| \leq 2 \cdot (256 \ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t})^{\ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t}}$. This implies that $S'$ is separable by a halfspace with the desired margin.
\end{enumerate}
\end{proof}

@@

\begin{proof}
%The proof the essentially the same as the proof of 
\begin{enumerate}
\item From Lemma~\ref{lem:rational-margin} and Theorem~\ref{thm:rational-norm}, 
we know that there exists some polynomial $p(x)$ of degree at most $(2\ceil{\log \frac 1 \gamma}+1) h(2t) t$, such that
$y p(x) \geq  2^{\ceil{\log \frac 1 \gamma}(\ceil{\log \frac 1 \gamma}-1)h(2t)t - 2}$ and 
$\|p\| \leq ((16\ceil{\log \frac 1 \gamma}+8) h(2t) t \cdot \frac 1 \gamma)^{(2\ceil{\log \frac 1 \gamma}+1)h(2t)t}$. 
By Lemma~\ref{lem:fm-convert}, there is some vector $c$, such that $y \inner{c, \phi_0(x)} = y p(x)$ for all $(x,y)$ in $S$	, and $\| c \| \leq 2^{\frac 1 2 \cdot (2\ceil{\log \frac 1 \gamma}+1) h(2t) t} \| p \|$.
This implies that $S'$ is separable by a halfspace with the desired margin.
